\todo{Something} presents OpenAdcess

### 2017-02-17 aesthetics.tex
what if life is just some hard equation &c &c

We should have a page that uses pretentious Clement Greenberg-esque language to talk about "perspective" and "foreground" and "background" and "depth of field" and so forth. Most papers are pretty boring: a bird's eye view. But as Freeman Dyson notes, there are birds and frogs in research. And frogs like to get in the mud. And frogs like to croak about Budweiser.

@@

>>>>

We should have a page that uses pretentious Clement Greenberg-esque language to talk about "perspective" and "foreground" and "background" and "depth of field" and so forth. Most papers are pretty boring: a bird's eye view. But as Freeman Dyson notes, there are birds and frogs in research. And frogs like to get in the mud. And frogs like to croak about Budweiser. And frogs are in the background.

@@

guide to april fools day pranks that won't embarrass your teen
old faithful superior accuracy as computer clock
old glory which thought was old faithful but retain for it superior

Academics can get around laws through fair use
good: HEY KIDS learn how JOE CAMEL targeted kids and got them to see how COOL smoking can be
bad (challenges authority): number theorists wrote a paper on the number-theoretic properties of "the nuclear code" numbers
